\cvsection{Experience}

\begin{cventries}
  \cventry
    {Freelance Fullstack Developer} % Job title
    {Freelance} % Organization
    {Lille, France - Remote} % Location
    {September 2023 - Today} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation of modern web applications using React, Next.js, Astro, Svelte, Typescript, TailwindCSS, ...}
        \item {Back-end development with Node.js, DB (SQL and noSQL).}
        \item {In collaboration with customers, I listen to their specific needs, to meet them as best I can. (Professionals and individuals)}
        \item {Technical support to guarantee product quality.}
        \item {Technology watch to keep abreast of the latest frameworks and technologies.}
      \end{cvitems}
    }

  \cventry
    {Frontend Developer} % Job title
    {Renex - Freelance} % Organization
    {Marly, France - Remote} % Location
    {May 2024 - June 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation and implementation of a new landing page (Figma).}
        \item {Maintenance and optimisation of the project (WordPress).}
      \end{cvitems}
    }  

  \cventry
    {Frontend Developer} % Job title
    {Ex-nihilo.agency - Freelance} % Organization
    {Lille, France - Remote} % Location
    {February 2024 - March 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Front-end development of the agency's showcase site (React, Next.js, Typescript, TailwindCSS, Framer-motion).}
        \item {Contribution to the design of the website for an optimal user experience, while respecting the customer's requirements.}
        \item {Technical SEO optimization.}
      \end{cvitems}
    }

  \cventry
    {Fullstack developer} % Job title
    {Smile} % Organization
    {Lille, France - Hybrid} % Location
    {January 2023 - June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation of customized web solutions for customers ranging from small businesses to large organizations.}
        \item {Close collaboration with customers to best meet their needs.}
        \item {Design of modern, innovative front-ends based on the ReactJS framework (ReactJS, NextJS, ThreeJS).}
        \item {Development of robust, scalable back-ends for optimum performance (NodeJS, Java).}
        \item {Adoption of best development practices such as Typescript, clean code, CI/CD (GitHub Actions) and deployment on AWS.}
      \end{cvitems}
    }

  % \cventry
  %   {Operations developer} % Job title
  %   {AXA} % Organization
  %   {Lille, France - Hybrid} % Location
  %   {October 2022 - December 2022} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Managed the release into production of various projects, ensuring a smooth transition between testing, pre-production and production environments, ensuring optimal availability and performance. (Azure DevOps)}
  %       \item {Agile resolution of operational issues, including proactive management of bug reports and fluid communication with development teams.}
  %       \item {Development of tailor-made Python scripts aimed at automating and optimizing the team's daily tasks.}
  %       \item {Technical assistance on ReactJS projects, contributing to the implementation of innovative and effective solutions.}
  %     \end{cvitems}
  %   }

  \cventry
    {Java DevOps Intern} % Job title
    {Sopra Banking Software} % Organization
    {Saint-Herblain, France - Hybrid} % Location
    {March 2022 - September 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and implementation of a cloud-native software in the banking sector with a microservice architecture (Java, Angular, Kubernetes, GitLab CI, Kube, Tests) in collaboration with the international (India), all in a DevOps environment.}
        \item {Security audit resolution}
        \item {Practice of the agile SCRUM cycle}
      \end{cvitems}
    }
    
% Need to gain some space
%   \cventry
%     {Software engineer intern} % Job title
%     {Orchestra} % Organization
%     {Luxembourg, Luxembourg - Remote} % Location
%     {August 2021 - September 2021} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Designed a web application for the Luxembourg surety mutual (Luxembourg Chamber of Commerce) using Figma}
%         \item {Experimented and realized the back-end and front-end of this web application, using WebDev}
%       \end{cvitems}
%     }

%   \cventry
%     {Software engineer intern} % Job title
%     {Eurogroup} % Organization
%     {Luxembourg, Luxembourg - Remote} % Location
%     {June 2016 - July 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Digitized files for the Luxembourg Chamber of Commerce}
%       \end{cvitems}
%     }

\end{cventries}
